\documentclass[paper=a4, fontsize=11pt]{scrartcl}
\usepackage[T1]{fontenc}
\usepackage{fourier}

\usepackage[english]{babel}															% English language/hyphenation
\usepackage[protrusion=true,expansion=true]{microtype}
\usepackage{amsmath,amsfonts,amsthm} % Math packages
\usepackage[pdftex]{graphicx}
\usepackage{url}


%%% Custom sectioning
\usepackage{sectsty}
\allsectionsfont{\centering \normalfont\scshape}


%%% Custom headers/footers (fancyhdr package)
\usepackage{fancyhdr}
\pagestyle{fancyplain}
\fancyhead{}											% No page header
\fancyfoot[L]{}											% Empty
\fancyfoot[C]{}											% Empty
\fancyfoot[R]{\thepage}									% Pagenumbering
\renewcommand{\headrulewidth}{0pt}			% Remove header underlines
\renewcommand{\footrulewidth}{0pt}				% Remove footer underlines
\setlength{\headheight}{13.6pt}


%%% Equation and float numbering
\numberwithin{equation}{section}		% Equationnumbering: section.eq#
\numberwithin{figure}{section}			% Figurenumbering: section.fig#
\numberwithin{table}{section}				% Tablenumbering: section.tab#


%%% Maketitle metadata
\newcommand{\horrule}[1]{\rule{\linewidth}{#1}} 	% Horizontal rule

\title{
  %\vspace{-1in}
  \usefont{OT1}{bch}{b}{n}
  \horrule{0.5pt} \\[0.4cm]
  \huge Cache Friendly Shuffles for Machine Learning
  \horrule{2pt} \\[0.5cm]
}
\author{
  \normalfont 								\normalsize
  \\[-3pt]
  \normalsize
  \today
}
\date{}


%%% Begin document
\begin{document}

\maketitle
\section{Overview}
\newpage
\section{Least Squares}
\newpage
\section{Word Embeddings}
\subsection{Introduction}
In the word embeddings problem, given context counts $X_{w,w'}$ we want to find word vectors
$v_{w} \in \mathbb{R}^{k}$ that minimizes the loss:
$$
min_{v,C}\sum_{w,w'}X_{w,w'}(log(X_{w,w'}) - \|v_w+v_{w'}\|^2 - C)^2
$$
\subsection{Experiment Details}
We ran our experiments on the Edison compute nodes which feature two
twelve core 2.4 GHz processors. However, we used only up to twelve
cores/threads to avoid effects of NUMA. Word vectors were length 100
double arrays.
\\\\
We used the first $10^9$ bytes of English Wikipedia from
http://mattmahoney.net/dc/textdata as corpus data. After running the text
preprocessing script supplied by the link, we computed co-occurrence
counts of pairs of distinct words to create the parameter dependence graph.
This graph was then fed into gpmetis, computing a min-k-cut partitioning to
create a cache-friendly ordering of the datapoints. k was set such that each
block of k datapoints would reference just enough word vectors to fit into the
L1-cache.
\\\\
Hogwild was then run on the permuted co-occurrence graph generated by gpmetis,
maintaining the same ordering throughout execution. Although we experimented with
both data sharding and no-data sharding, only results from data sharding are presented.
To test hogwild without a cache-friendly shuffle, we randomly shuffled the datapoints before execution.
\\\\
We also ran the experiments on subsets of the corpus, repeating the
procedure on the first $10\%$, $25\%$, $50\%$ and $75\%$ of the corpus data.
In the full corpus data, there were $~200,000$ word vectors, and $~30,000,000$
datapoints.
\\\\

\newpage
\section{Conclusion}
\newpage
\section{Future}
\end{document}
